### 2018-11-27 zst/data/reference.tex
update

@@

>>>>

\bibitem{syc-1}
武斌. 基于符号计算方法的程序验证技术研究[D]. 华东师范大学, 2010.

\bibitem{syc-3}
Strang G, Strang G, Strang G, et al. Introduction to linear algebra[M]. Wellesley, MA: Wellesley-Cambridge Press, 1993.

\bibitem{syc-5}
张韵华. 符号计算系统 Mathematica 教程[M]. 科学出版社, 2001.

\bibitem{syc-8}
Xu G. Searching for Painlevé integrable conditions of nonlinear PDEs with constant parameters using symbolic computation[J]. Computer Physics Communications, 2008, 178(7): 505-517.

\bibitem{syc-11}
李宏哲. 基于符号计算的 WBK 及其相关方程的达布变换构造和孤子解研究[D]. 北京邮电大学, 2010.

\bibitem{syc-12}
张冬华. 非线性发展方程和孤波解的研究[D]. 北京: 北京邮电大学, 2007.

\bibitem{syc-14}
Liang S, Jeffrey D J. Automatic computation of the travelling wave solutions to nonlinear PDEs[J]. Computer Physics Communications, 2008, 178(9): 700-712.

\bibitem{syc-17}
Zabusky N J, Kruskal M D. Interaction of" solitons" in a collisionless plasma and the recurrence of initial states[J]. Physical review letters, 1965, 15(6): 240.

\bibitem{syc-18}
Gardner C S, Greene J M, Kruskal M D, et al. Method for solving the Korteweg-deVries equation[J]. Physical review letters, 1967, 19(19): 1095.

\bibitem{ss-39}
Mu G, Qin Z. Dynamic patterns of high-order rogue waves for Sasa–Satsuma equation[J]. Nonlinear Analysis: Real World Applications, 2016, 31: 179-209.

\bibitem{ss-40}
Chen S. Twisted rogue-wave pairs in the Sasa-Satsuma equation[J]. Physical Review E, 2013, 88(2): 023202.

\bibitem{ss-41}
Akhmediev N, Soto-Crespo J M, Devine N, et al. Rogue wave spectra of the Sasa–Satsuma equation[J]. Physica D: Nonlinear Phenomena, 2015, 294: 37-42.

@@

\bibitem{nss-1}
Ablowitz M J, Musslimani Z H. Integrable nonlocal nonlinear Schrödinger equation[J]. Physical review letters, 2013, 110(6): 064105.

\bibitem{nss-2}
Yang B, Yang J. Transformations between nonlocal and local integrable equations[J]. Studies in Applied Mathematics, 2018, 140(2): 178-201.

\bibitem{nss-3}
Ma L, Zhao H, Gu H. Integrability and gauge equivalence of the reverse space–time nonlocal Sasa–Satsuma equation[J]. Nonlinear Dynamics, 2018, 91(3): 1909-1920.
